\normalfont\spacedallcaps{Hazardous asteroids forecast via Markov random fields}

### 2021-11-11 Manuscript/manuscript.tex
PUB

In this section we are going to review the theoretical concepts that underlies to the probabilistic methods here used as well to the physical laws that describe the dynamics of the asteroids.  Concerning the methods,  we will expose them following the approaches of Murphy \cite{murphy2012machine},  Koller  \cite{koller2009probabilistic} and Russel \cite{russell2010artificial}.  Furthermore we will provide also a rapid overview of the main concepts of information theory,  since we used some of its concepts in the preliminary analysis of the dataset.  On the other side for the concepts related to the celestial mechanics we will follow the Murray textbook \cite{murray1999solar}.

@@

where $\beta$ is proportional to the inverse of the system temperature.  Coming back the unnormalized probability of a collective state $\textbf{y}$,  if we set $\Sigma^{-1}=\textbf{W}$, $\boldsymbol{\mu}=boldsymbol{\Sigma} b$ and $c=\dfrac{1}{2}\mu^{T}\boldsymbol{\Sigma}^{-1}\mu$ we obtain a Gaussian \cite{murray1999solar}:

>>>>

In this section we are going to review the theoretical concepts that underlies to the probabilistic methods here used as well to the physical laws that describe the dynamics of the asteroids.  Concerning the methods,  we will expose them following the approaches of Murphy \cite{murphy2012machine},  Koller  \cite{koller2009probabilistic} and Russel \cite{russell2010artificial}.  Furthermore we will provide also a rapid overview of the main concepts of information theory,  following the Cover \cite{cover2006elements} and MacKay \cite{mackay2003information} approaches ,  since we used some of its concepts in the preliminary analysis of the dataset.  On the other side for the concepts related to the celestial mechanics we will follow the Murray textbook \cite{murray1999solar}.

@@

where $\beta$ is proportional to the inverse of the system temperature.  Coming back the unnormalized probability of a collective state $\textbf{y}$,  if we set $\Sigma^{-1}=\textbf{W}$,  $\boldsymbol{\mu}=\boldsymbol{\Sigma} \textbf{b}$ and $c=\dfrac{1}{2}\mu^{T}\boldsymbol{\Sigma}^{-1}\mu$ we obtain a Gaussian \cite{murray1999solar}:

### 2021-11-11 Manuscript/structure.tex
PUB

\hypersetup{
%draft, % Uncomment to remove all links (useful for printing in black and white)
colorlinks=true, breaklinks=true, bookmarks=true,bookmarksnumbered,
urlcolor=webbrown, linkcolor=RoyalBlue, citecolor=webgreen, % Link colors
pdftitle={Association analysis and tweets}, % PDF title
pdfauthor={\textcopyright Martina Corsini, Marzio De Corato}, % PDF Author
pdfsubject={Project for the course Algorithms for massive datasets (DSE) - DSE}, % PDF Subject
pdfkeywords={}, % PDF Keywords
pdfcreator={pdfLaTeX}, % PDF Creator
pdfproducer={LaTeX with hyperref and ClassicThesis} % PDF producer
}

>>>>

\hypersetup{
%draft, % Uncomment to remove all links (useful for printing in black and white)
colorlinks=true, breaklinks=true, bookmarks=true,bookmarksnumbered,
urlcolor=webbrown, linkcolor=RoyalBlue, citecolor=webgreen, % Link colors
pdftitle={Hazardous asteroids forecast via Markov random fields}, % PDF title
pdfauthor={\textcopyright Marzio De Corato}, % PDF Author
pdfsubject={Project for the course Probabilistic modelling (DSE)}, % PDF Subject
pdfkeywords={}, % PDF Keywords
pdfcreator={pdfLaTeX}, % PDF Creator
pdfproducer={LaTeX with hyperref and ClassicThesis} % PDF producer
}
